Monitoring and Projecting Global Hunger: Are We On Track?

### 2021-01-26 docs/modeling_fies.tex
Updates from Overleaf

\maketitle
\begin{abstract}
Using microdata from 75 countries collected by FAO through the Gallup World Poll for the Voices of the Hungry project, we modeled levels of food security at the subnational level from 2010 to 2030 to create the World Hunger Clock (https://worldhunger.io).  This is the first global picture of food security at a subnational level based on the Food Insecurity Experience Scale, the indicator for the Sustainable Development Goal of "Zero Hunger" that is most indicative of the individual's lived experience of food insecurity and hunger.  We find significant heterogeneity in food security around the world, ranging from less than 4\% of the population being at least moderately food insecure in some high-income countries to parts of the developing world where over half the population is severely food insecure.  Examining global temporal trends and accounting for the effects of the COVID-19 pandemic, we find that rates of severe food insecurity are declining steadily yet slowly, with larger observed and forecasted gains in lower and lower-middle income countries, resulting in global decreases in the total number of severely food insecure people.  However, the total number of moderately food insecure people has been increasing and, after recovering from the shock of the COVID-19 pandemic, we predict it will continue to increase through the end of the 2020s.  Overall, we conclude that global gains have been incremental, and current trends in development and demographic change will still leave a large share of the world's population still experiencing hunger by 2030.  \end{abstract}

>>>>

\maketitle
\begin{abstract}
This paper presents the first global picture of food security at a subnational level based on the Food Insecurity Experience Scale, the indicator for the Sustainable Development Goal of ``Zero Hunger" that is most indicative of the individual's lived experience of food insecurity and hunger.  Using microdata from 75 countries and filling gaps using machine learning, we find significant heterogeneity in levels of food insecurity around the world.  Examining global temporal trends and accounting for the effects of the COVID-19 pandemic, we find that rates of severe food insecurity are declining, resulting in global decreases in the total number of severely food insecure people.  However, the total number of moderately food insecure people has been increasing and, after recovering from the shock of the COVID-19 pandemic, we predict it will continue to increase through the end of the 2020s.  Overall, we conclude that current trends in development and demographic change will still leave a large share of the world's population still experiencing hunger by 2030.  \end{abstract}

\textit{Keywords: Food Security, Sustainable Development Goal 2, Machine Learning, Food Insecurity Experience Scale, Projections}
